How vanishing web-based tools hamper reproducibility

### 2023-12-12 manuscript/letter.Rmd
abstract

>>>>

## Abstract

Web-based tools are an indispensable resource for conducting genomic and bioinformatics analysis, but if they disappear
it can leave reproducibility gaps in research projects.
Unless such tools allow for preservation of key materials for reproduction, researchers may unwittingly be in breach of
data management mandates.

## Main text
